|

### 2020-10-13 manuscript/article.Rmd
small edits

---
title:  |
        | Financial Incentives and Health Care Prevention: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
author: 
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Louise Araújo, Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments. Special thanks to XXXX for their excellent research assistance. Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
abstract:    |
    | __Objectives.__ To quantify the impact of individual and collective monetary rewards on the performance of health care workers assigned to find and exterminate *Aedes aegypti*, as well as their effect on dengue hospitalisations. 
    | __Methods.__ We hired and trained subjects to visit households, find *A. aegypti* breeding sites, and exterminate mosquito larvae in the city of Rio Verde, Brazil, in May 2018. We provided individual and team bonuses to the two treatment groups, whereas the control group received a flat compensation for completing their tasks.
    | __Results.__ Financial bonuses increased the number of cleaned breeding sites in both treatment status (individual and team bonuses) and team bonuses also improved larvae extermination. The intervention decreased the disease incidence in 10.3%, but the findings are not statistically significant across all model specifications.
    | __Conclusions.__ Performance bonuses improve productivity in public service provision, yet more research is needed to asssess whether higher health care worker performance decreases dengue hospitalisations.
    | __Public Health Implications.__ *A. aegypti* control programmes may benefit from alternative compensation schemes, specially when provided to teams. For this strategy to succeed, financial incentives have to be distributed widely as their aggregate effect is limited.
abstractspacing: onehalf
keywords: Aedes aegypti, dengue, financial incentives, mosquito control, randomised field experiment, preventive health care
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

@@

We conducted a randomised field trial in Rio Verde, a municipality in the
Brazilian Midwestern state of Goiás. Rio Verde had 229,000 inhabitants and 1,156
confirmed dengue cases, one of highest counts in the state [@goias2020]. We used
Facebook advertisements to recruit potential participants. The advertisements
directed applicants to Google Forms, where we asked for their contact
information. We sent a pre-treatment demographic survey to every applicant who
provided a valid email address. At this stage, we excluded all individuals under
18 years old. We invited the remaining applicants to our training session, which
we ran on the 4^th^ of May, 2018. The meeting consisted of a lecture on *A.
aegypti* vector biology and practical instructions on how to find and
exterminate mosquito breeding sites. Those who did not attend the session were
also excluded from the study.

@@

The intervention took place on the 5^th^ of May, 2018. We randomly assigned
subjects into three groups and directed each group to separate headquarters in
order to avoid spillovers. In the control group ($n = 68$), we told
participants that they would receive a flat payment regardless of their
performance (BRL 110 / USD 20 per subject). In the individual treatment group
($n = 68$), we informed subjects that we would rank individual performances and
double the compensation for those who performed above the sample median (BRL
220 / USD 50 per subject). In the collective treatment group ($n = 70$), we
explained that we would rank the pair performance and double the payment for
teams who presented results better than the sample median (BRL 220 / USD 50 per
subject). Participants worked in pairs and were aware of other groups, but they
did not know about the different treatment conditions. The teams received a
leaflet with a map of the area they should cover. The route comprised of two to
three blocks and contained around 120 houses.

@@

The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX]) if we take
both treatments and compare them with the control group. The result is
consistent around fewer weeks before and after the intervention, but it does
not reach conventional levels of statistical significance. This suggests that
the treatment effect is probably small. The comparison between the two
treatment statuses show an impact of 2.9\% (CI: [XXX, XXX]) fewer infections in
the collective bonus group. However, the result is also not statistically
significant.

@@

The study has important limitations. First, we ran our experiment for a small
period of time and in a particular Brazilian city, thus the findings may not
generalise to other locations. Second, our experiment needed a longer and wider
coverage to measure whether the treatment has a significant impact on dengue
incidence, as the effect seems smaller than expected. Third, we included a
post-treatment adjustment to ensure the balance of our territorial variables.
Although using matching estimators to improve balance is in line with the best
statistical practices, it requires additional assumptions. Finally, the
experiment only measures the impact of financial rewards on worker performance,
and it does not assess the effect of non-monetary incentives, such as
motivational messages or constant feedback, which may be useful alternatives in
jurisdictions where legal or financial constraints may prevent the government
from distributing financial bonuses to civil servants.

>>>>

---
title:  |
        | Financial Incentives and Health Care Prevention: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
author: 
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Louise Araújo, Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments. Special thanks to XXXX for their excellent research assistance. Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
abstract:    |
    | __Objectives.__ To quantify the impact of individual and collective monetary rewards on the performance of health care workers assigned to find and exterminate *Aedes aegypti*, as well as their effect on dengue hospitalisations. 
    | __Methods.__ We hired and trained subjects to visit households, find *A. aegypti* breeding sites, and exterminate mosquito larvae in the city of Rio Verde, Brazil, in May 2018. We provided individual and team bonuses to the two treatment groups, whereas the control group received a flat compensation for completing their tasks.
    | __Results.__ Financial bonuses increased the number of cleaned breeding sites in both treatment status (individual and team bonuses) and team bonuses also improved larvae extermination. The intervention decreased the disease incidence in 10.3%, but the findings are not statistically significant across all model specifications.
    | __Conclusions.__ Performance bonuses improve productivity in public service provision, yet more research is needed to asssess whether higher health care worker performance decreases dengue hospitalisations.
    | __Public Health Implications.__ *A. aegypti* control programmes may benefit from alternative compensation schemes, specially when provided to teams. For this strategy to succeed, financial incentives have to be distributed widely as their aggregate effect is limited.
abstractspacing: single
keywords: Aedes aegypti, dengue, financial incentives, mosquito control, randomised field experiment, preventive health care
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

@@

We conducted a randomised field trial in Rio Verde, a municipality in the
Brazilian Midwestern state of Goiás. Rio Verde had 229,000 inhabitants and
1,156 confirmed dengue cases, one of highest counts in the state [@goias2020].
We used Facebook advertisements to recruit potential participants. The
advertisements directed applicants to Google Forms, where we asked for their
contact information. We sent a pre-treatment demographic survey to every
applicant who provided a valid email address. At this stage, we excluded all
individuals under 18 years old and invited the remaining applicants to our
training session, which we ran on the 4^th^ of May, 2018. The meeting consisted
of a lecture on *A. aegypti* vector biology and practical instructions on how
to find and exterminate mosquito breeding sites. Those who did not attend the
session were also excluded from the study.

@@

The intervention took place on the 5^th^ of May, 2018. We randomly assigned
subjects into three groups and directed each group to separate headquarters in
order to avoid spillovers. In the control group ($n = 68$), we told
participants that they would receive a flat payment regardless of their
performance (BRL 110 / USD 25 per subject). In the individual treatment group
($n = 68$), we informed subjects that we would rank individual performances and
double the compensation for those who performed above the sample median (BRL
220 / USD 50 per subject). In the collective treatment group ($n = 70$), we
explained that we would rank the pair performance and double the payment for
teams who presented results better than the sample median (BRL 220 / USD 50 per
subject). Participants worked in pairs and were aware of other groups, but they
did not know about the different treatment conditions. The teams received a
leaflet with a map of the area they should cover. The route comprised of two to
three blocks and contained around 120 houses.

@@

The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX]) if we take
both treatments together and compare them with the control group. The result is
consistent around fewer weeks before and after the intervention, but it does
not reach conventional levels of statistical significance. This suggests that
the treatment effect is probably small. The comparison between the two
treatment statuses show an impact of 2.9\% (CI: [XXX, XXX]) fewer infections in
the collective bonus group. However, the result is also not statistically
significant.

@@

The study has several limitations. First, we ran our experiment for a small
period of time and in a particular Brazilian city, thus the findings may not
generalise to other locations. Second, our experiment needed a longer and wider
coverage to measure whether the treatment has a significant impact on dengue
incidence, as the effect seems smaller than expected. Third, we included a
post-treatment adjustment to ensure the balance of our territorial variables.
Although using matching estimators to improve balance is in line with the best
statistical practices, it requires additional assumptions. Finally, the
experiment only measures the impact of financial rewards on worker performance,
and it does not assess the effect of non-monetary incentives, such as
motivational messages or constant feedback, which may be useful alternatives in
jurisdictions where legal or financial constraints may prevent the government
from distributing financial bonuses to civil servants.
